Fair Queuing Aware Congestion Control

### 2022-06-21 tex/paper.tex
Update pdf

\documentclass[conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage{dblfloatfix}
\renewcommand{\thefootnote}{\arabic{footnote}}
\renewcommand{\thempfootnote}{\arabic{mpfootnote}}
\begin{document}

@@

We also evaluated the performance of our fair queuing detection on a bottleneck managed by fq\_codel \cite{hoeiland-joergensen_flow_2018}. 
We chose a default target queuing delay of 10\,ms following Apple's implementation\footnote{
    \url{https://github.com/apple/darwin-xnu/blob/main/bsd/net/if.h\#L262}
} because we argue that Apple probably spent a considerable amount of time fine-tuning their implementation and 
came to the conclusion that 10\,ms work best as the default target delay.

>>>>

\documentclass[conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{subfig}
\usepackage{tabularx}
\usepackage{dblfloatfix}
\usepackage{xurl}

\renewcommand{\thefootnote}{\arabic{footnote}}
\renewcommand{\thempfootnote}{\arabic{mpfootnote}}
\begin{document}

@@

We also evaluated the performance of our fair queuing detection on a bottleneck managed by fq\_codel \cite{hoeiland-joergensen_flow_2018}. 
We chose a default target queuing delay of 10\,ms following Apple's implementation\footnote{
    \url{https://github.com/apple/darwin-xnu/blob/2ff845c2e033bd0ff64b5b6aa6063a1f8f65aa32/bsd/net/if.h\#L262}
} because we argue that Apple probably spent a considerable amount of time fine-tuning their implementation and 
came to the conclusion that 10\,ms work best as the default target delay.
